---
output:
  md_document:
    variant: markdown_github
    includes:
      in_header: header.md
    toc: true
    toc_depth: 4
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(digits = 4)
library(magrittr)
```

# Repository Structure

```{r dirs_setup}
library(data.tree) # install.packages("data.tree")
dir_node <- yaml::yaml.load_file("repo_structure.yaml") %>% as.Node
```

```{r dirs_create}
dir_df <- ToDataFrameTable(dir_node, "pathString", "type")
dir_df$pathString <- sub("Repository Structure/", "", dir_df$pathString, fixed = TRUE)
invisible(sapply(dir_df$pathString[dir_df$type == "directory"], function(path) {
  if (!dir.exists(path)) {
    dir.create(path, recursive = TRUE)
  }
}))
```

```{r dirs_document, results = 'asis'}
dir_df <- ToDataFrameTree(dir_node, "pathString", "type", "description")
output <- paste0(
  gsub(
    "- ", "- [", # Complete links
    paste0( # Make partial links
      gsub(" --", "- ", # Markdown list item formatting
           gsub("¦", " ", # Fix markdown list item spacing
                gsub("°", "", # BEGIN: Remove node symbols
                     paste0(
                       stringi::stri_trim_right(dir_df$levelName),
                       ifelse(dir_df$type == "directory", "/", "")
                     ),
                     fixed = TRUE), # END: Remove node symbols
                fixed = TRUE), # END: Fix markdown list item spacing
           fixed = TRUE), # END: Markdown list item formatting
      "](", sub("Repository Structure/", "", dir_df$pathString, fixed = TRUE), ")"
      ), # END: Make partial links
    fixed = TRUE), # END: Complete links
  " : ", dir_df$description
)
cat(paste0(output[-1], collapse = "\n"))
```

# Data

The searches are sampled on a per-user basis. That is, first we sample 1% of unique user agent (UA) and IP address pairs. Then we get all the search requests made by those users, instead of sampling 1% of the search requests. This way, we can use the sample to determine things like: number of searches performed per hour or day, median time between consecutive searches, and variance of query features.

# License

This work is licensed under a <a rel="license" href="http://creativecommons.org/licenses/by/4.0/">Creative Commons Attribution 4.0 International License</a>.
